---
title: "HMMVMS"
substitle: ""
abstract: "" 
author: Gilles Guillot, Pierre Benoit, Savvas Kinalis, Francois Bastardie, Valerio Bartolino
date: "`r Sys.time()`"
output:
  rmarkdown::html_vignette:
  #pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
vignette: >
  %\VignetteIndexEntry{HMMVMS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=FALSE,
  comment = "#>"
)
```

```{r setup}
#library(HMMVMS)
```




# Overview
This page provides information about the computer program HMMVMS, an R package for detecting fishing activity from VMS data.










# References
The model and algorithm underlying the HMMVMS program are described in 

* Guillot, Gilles, Pierre Benoit, Savvas Kinalis, François Bastardie, and Valerio Bartolino. "Enhancing and comparing methods for the detection of fishing activity from Vessel Monitoring System data." arXiv preprint [arXiv:1708.09663](https://arxiv.org/abs/1708.09663) (2017). 

 